### 2022-06-16 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a486162393bdd46cba57058d9855197a42bd9b0c 🚀

As host richness, joint disctinveness, or phylogeographic structure
suggest that the bat/betacoronavirus complex is globally fragmented
enough to give rise to both different levels of risk (as evidenced by
the spatial location of spillover events) and different types of
co-evolutionary dynamics, we turn to the Geographic Mosaic Theory of
Coevolution \textbf{REF} to provide a measure of risk accounting for
multiple processes. In fig.~\ref{fig:trivariate}, we overlapped three
components of spillover risk: viral sharing, \emph{i.e.} the chance that
two bats will share viruses overall; Local Contribution to Beta
Diversity, \emph{i.e.} the fact that a bat community is compositionally
unique compared to the average compositional similarity across the
entire system; finally, host phylogenetic diversity, \emph{i.e.} how
dispersed the bats in a location are within the tree of life. This
approach leads to the definition of broad biogeographic regions of risk,
where the same color represents the same type of risk. By way of
constrat to figures fig.~\ref{fig:richness} and fig.~\ref{fig:biogeo},
these regions do not necessarilly overlap with previous spatial
partitions of the bat/betacoronavirus complex.

>>>>

As host richness, joint disctinveness, or phylogeographic structure
suggest that the bat/betacoronavirus complex is globally fragmented
enough to give rise to both different levels of risk (as evidenced by
the spatial location of spillover events) and different types of
co-evolutionary dynamics, we turn to the Geographic Mosaic Theory of
Coevolution (Thompson 2005) to provide a measure of risk accounting for
multiple processes. In fig.~\ref{fig:trivariate}, we overlapped three
components of spillover risk: viral sharing, \emph{i.e.} the chance that
two bats will share viruses overall; Local Contribution to Beta
Diversity, \emph{i.e.} the fact that a bat community is compositionally
unique compared to the average compositional similarity across the
entire system; finally, host phylogenetic diversity, \emph{i.e.} how
dispersed the bats in a location are within the tree of life. This
approach leads to the definition of broad biogeographic regions of risk,
where the same color represents the same type of risk. By way of
constrat to figures fig.~\ref{fig:richness} and fig.~\ref{fig:biogeo},
these regions do not necessarilly overlap with previous spatial
partitions of the bat/betacoronavirus complex.
